%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Sean Richardson Hardjanto} \\ \vspace{1pt}
    \small (+65) 85498290 $|$ 
    \href{mailto:seanhardjanto034@gmail.com}{\underline{seanhardjanto034@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/sean-hardjanto}{\underline{linkedin.com/in/sean-hardjanto}} $|$
    \href{https://34cats.com/}
    {\underline{34cats.com}} $|$
    \href{https://github.com/seanrh34}
    {\underline{github.com/seanrh34}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National University of Singapore}{Singapore}
      {Bachelor of Computing in Computer Science (Cumulative GPA: 4.54)}{Aug. 2024 -- Current}
    \resumeSubheading
      {Hwa Chong Institution}{Singapore}
      {GCE 'A'-Levels (Attained 85 Rank Points with 4H2s)}{Feb. 2020 -- Dec 2021}
    \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
    \resumeSubHeadingListStart

    \resumeSubheading
    {CS1101S: Programming Methodology 1 Teaching Assistant}{Aug 2025 - Dec 2025}
    {National University of Singapore}{Singapore}
        \resumeItemListStart
        \resumeItem{Facilitated group discussions among students to let them apply their knowledge of the subject.}
        \resumeItem{Provided personalized support for concepts that are harder to grasp and grading of students' work.}
        \resumeItemListEnd

    \resumeSubheading
        {Web Development and Digital Marketing Intern}{Mar 2024 - Jul 2024}
        {Guidesify Pte. Ltd}{Singapore}
        \resumeItemListStart
            \resumeItem{Developed a WordPress post manager to simplify posting articles to WordPress sites and an AI Post Writer to write SEO-optimised articles with Telegram integration.}
            \resumeItem{Developed a company UEN Search web application using REST APIs, which greatly boosted the Guidesify's domain's traffic.}
    \resumeItemListEnd
        
    \resumeSubheading
      {Multilingual Transcriptionist}{Jan 2022 - Feb 2022}
      {Nanyang Technological University (NTU)}{Singapore}
      \resumeItemListStart
        \resumeItem{ Transcribed audio recordings of conversations into text in Bahasa Indonesia where some of the
        conversations included regional languages such as Javanese and Sundanese for NTU's AI speech-to-text project.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd
%-----------Co-Curricular Activities-----------
\section{Co-Curricular Activities}
    \resumeSubHeadingListStart

    \resumeSubheading
    {Logistics Executive}{Mar 2025 - Feb 2026}
    {NUS Fencing Club}{Singapore}
        \resumeItemListStart
        \resumeItem{Procured equipment and liaised with external organizations for the clubs' operational needs.}
        \resumeItem{Organized NUS Fencing Challenge 2025, an inter-tertiary Fencing competition attended by over 260 fencers, both local and international, overseeing the delivery of logistics and co-ordination with external partners.}
        \resumeItemListEnd

    \resumeSubheading
        {Vice Project Director}{Sep 2024 - Aug 2025}
        {Ridge View Freshmen Orientation Programme 2025}{Singapore}
        \resumeItemListStart
            \resumeItem{Managed external relations with vendor and sponsors as well as coordinated and planned the orientation programme for over 260 freshmen as participants and 90 seniors as helpers.}
            \resumeItem{Developed Ventera ScoreBot, a Telegram bot for live points tracking and updating used by the participants and organisers respectively.}
    \resumeItemListEnd

    \resumeSubHeadingListEnd
%-----------SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \item \small{
    \textbf{Programming Languages}{: JavaScript/TypeScript with HTML + CSS, Python, Java} \\
    \textbf{Frameworks and Tools}{: Node.js, Svelte, SvelteKit, React, Next.js, Tailwind, JavaFX, MkDocs} \\
    \textbf{Developer Tools}{: VS Code, Visual Studio, PyCharm, Jupyter, IntelliJ, Git, PostgreSQL, Supabase, Lexical} \\
    \textbf{Certifications}{: ITIL Foundation Certificate in IT Service Management by Axelos }
  }
\end{itemize}

%-----------Relevant Links and Past Works-----------
\section{Relevant Projects}
\begin{itemize}[leftmargin=0.15in, label={}]
  \item \small{
    \textbf{Guidesify GenAI SEO Writer App}{: }\href{https://app.guidesify.com/genai-seo-writer}{https://app.guidesify.com/genai-seo-writer} \\
    \textbf{Guidesify UEN Search App}{: }\href{https://app.guidesify.com/uen-search}{https://app.guidesify.com/uen-search} \\
    \textbf{Guidesify Apps Documentation Site}{: }\href{https://docs.guidesify.com}{https://docs.guidesify.com} \\
    \textbf{DozeBusters Web App for Hack\&Roll 2025}{: }\href{https://devpost.com/software/dozebuster}{https://devpost.com/software/dozebuster} \\
    \textbf{NUS Buffet App for Orbital 2025}{: }\href{https://github.com/seanrh34/team-yes-7198}{https://github.com/seanrh34/team-yes-7198} \\
    \textbf{PawPress CMS}{: }\href{https://blog.34cats.com/}
    {https://blog.34cats.com} \\
    \textbf{Ventera ScoreBot}{: }\href{https://github.com/seanrh34/ventera-scorebot-v2}
    {https://github.com/seanrh34/ventera-scorebot-v2} \\
  }
\end{itemize}
\end{document}
